\thesistitle

### 2019-08-18 sections/related_work.tex
PRI

Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} propose a tool to suggest refactorings for the clones found by the NiCAD tool \cite{roy2008nicad, cordy2011nicad}. This tool is named Duplicated Code Refactoring Advisor (DCRA). The DCRA suggests refactorings, based on Table~\ref{tab:relationrefactoring}, to clones found in Java projects.

@@

\subsection{Pattern‐based clone Refactoring Inspection (PRI)}

>>>>

Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} propose DCRA, a tool to suggest refactorings for the clones found by the NiCAD tool \cite{roy2008nicad, cordy2011nicad}. DCRA suggests refactorings to clones found in Java projects based on the mapping between relation and refactoring techniques shown in Table~\ref{tab:relationrefactoring}.

@@

\subsection{Pattern‐based clone Refactoring Inspection (PRI)}
A study by Chen et al.~\ref{chen2018clone} addresses the problem that developers cannot easily determine which clones can be refactored or how they should be maintained scattered
throughout a large code base in evolving systems. They propose PRI, a technique for managing clone refactorings for clones with a Sibling relation. PRI is a plugin for the Eclipse IDE that shows which refactoring techniques can be used to refactor clones. Because it is integrated in the Eclipse IDE, the refactorings can be executed largely automatically, as this IDE has a large set of tools for performing such transformations.

PRI traces clones through revisions of a software project. This makes this tool able to find incompletely refactored clones. PRI produces false positives in that several groups are incorrectly classified since the clone detector suffers the inaccuracy in finding semantically equivalent behaviors between clones.
